LayeredTypes

### 2022-10-07 paper/paper.tex

\lstinputlisting[language=Haskell,caption={Contracts in LiquidHaskell}, label={lst:liquidhaskell}]{BasicLT.hs}

@@

\lstinputlisting[language=Haskell,caption={Combining Refinement Types},label={lst:combined_refs}]{CombinedLT.hs}

>>>>

\lstinputlisting[caption={Contracts in LiquidHaskell}, label={lst:liquidhaskell}]{BasicLT.hs}

@@

\lstinputlisting[caption={Combining Refinement Types},label={lst:combined_refs}]{CombinedLT.hs}
